% !TEX root = FinalDeliverable.tex

\section{Dataset and Characteristics}
For the dataset of this study, we selected the top 100 Java projects in GitHub ranked according to the number of stars. In GitHub, when a user stars a project, it means that the user is:
\begin{itemize}
  \item Creating a bookmark for easier access
  \item Showing appreciation to the repository maintainer for their work
\end{itemize}

Therefore, by selecting the projects with higher number of stars, we are including those Java projects which are more liked and supported by the community of developers in GitHub. This includes projects like the Spring framework with which a lot of good developers are associated. As a result, building the probabilistic model based on a study of these projects would provide the benefit of making the model more reliable.
%, which may have a correlation with having a lot of followers, contributors and activity; and this diversity benefits our study since having a larger diversity of bug fixes, makes the model being built from this data more reliable and more diverse.

We restricted ourselves to studying only 20 recent commits because of time and storage limitations. Analyzing just 20 commits per project took a total of four days. Moreover, storing the before-fix and after-fix versions of each file in every commit for one project with about a 1000 commits required approximately 65GB of disk space. For these reasons, we have deferred a study of the full commit history of each of the projects as future work.

Determining whether a commit is a bug-fixing commit or not is usually done by applying a regular expression to the commit message. This method relies on the presence of certain words (that indicate that this commit might be related to a bug fix) and their order in the the commit message. We have used a regular expression that is similar to the one used by Boa~\cite{Dyer2013} in order to find bug-fixing commits. The regular expression that we have used is as follows:
\begin{itemize}
  \item "[Ff]ix(ed|es|ing)?(\textbackslash s)*([Bb]ug|[Ii]ssue|[Pp]roblem)?(s)?"
\end{itemize}

In order to ensure that the commits whose messages matched the above regular expression are actually bug-fixing commits, we performed the study in the following section.

\input{commit_validation}
